decompr: GVC decomposition in R

### 2015-01-16 draft.tex
put everything together

\documentclass{article}

@@

\title{decompr: GVC decomposition in R}
\author{Bastiaan Quast and Victor Kummritz}

\begin{document}
\maketitle

@@

<<load-package, message=FALSE >>=
# load the package
library(decompr)
@

<<load-data >>=
# load the data
data(leather)
# list the objects in the data set
ls()
@

@@

<<load_tables >>=
decompr_object <- load_tables_vectors( x = inter,
                                       y = final,
                                       k = countries,
                                       i = industries,
                                       o = out         )
@

We can now decompose the elements using the Leontief decomposition.
<<leontief >>=
lt <- leontief( decompr_object )
@

@@

<<leontief-wrapper >>=
lt2 <- decomp( x = inter,
               y = final,
               k = countries,
               i = industries,
               o = out,
               method = "leontief" )
@

@@

\subsection{Output}
<<lt-out, out.extra='angle=90' >>=
lt
@

@@

<<wwz >>=
w <- wwz(decompr_object)
@

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\title{decompr: GVC decomposition in R}
\author{Bastiaan Quast and Victor Kummritz}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
\maketitle

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# load the package}
\hlkwd{library}\hlstd{(decompr)}
\end{alltt}
\end{kframe}
\end{knitrout}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{# load the data}
\hlkwd{data}\hlstd{(leather)}
\hlcom{# list the objects in the data set}
\hlkwd{ls}\hlstd{()}
\end{alltt}
\begin{verbatim}
## [1] "countries"  "final"      "industries" "inter"      "out"
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{decompr_object} \hlkwb{<-} \hlkwd{load_tables_vectors}\hlstd{(} \hlkwc{x} \hlstd{= inter,}
                                       \hlkwc{y} \hlstd{= final,}
                                       \hlkwc{k} \hlstd{= countries,}
                                       \hlkwc{i} \hlstd{= industries,}
                                       \hlkwc{o} \hlstd{= out         )}
\end{alltt}
\end{kframe}
\end{knitrout}

We can now decompose the elements using the Leontief decomposition.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt} \hlkwb{<-} \hlkwd{leontief}\hlstd{( decompr_object )}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt2} \hlkwb{<-} \hlkwd{decomp}\hlstd{(} \hlkwc{x} \hlstd{= inter,}
               \hlkwc{y} \hlstd{= final,}
               \hlkwc{k} \hlstd{= countries,}
               \hlkwc{i} \hlstd{= industries,}
               \hlkwc{o} \hlstd{= out,}
               \hlkwc{method} \hlstd{=} \hlstr{"leontief"} \hlstd{)}
\end{alltt}
\end{kframe}
\end{knitrout}

@@

\subsection{Output}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{lt}
\end{alltt}
\begin{verbatim}
##                               Argentina.Agriculture
## Argentina.Agriculture                   28.52278143
## Argentina.Textile.and.Leather            1.06206936
## Argentina.Transport.Equipment            0.21043693
## Turkey.Agriculture                       0.71952151
## Turkey.Textile.and.Leather               0.41201175
## Turkey.Transport.Equipment               0.03482652
## Germany.Agriculture                      0.92530356
## Germany.Textile.and.Leather              0.64666560
## Germany.Transport.Equipment              0.66638333
##                               Argentina.Textile.and.Leather
## Argentina.Agriculture                            2.79395126
## Argentina.Textile.and.Leather                   19.12053186
## Argentina.Transport.Equipment                    0.14228369
## Turkey.Agriculture                               1.34237213
## Turkey.Textile.and.Leather                       1.38523849
## Turkey.Transport.Equipment                       0.08553139
## Germany.Agriculture                              2.25142713
## Germany.Textile.and.Leather                      0.72785683
## Germany.Transport.Equipment                      0.65080723
##                               Argentina.Transport.Equipment
## Argentina.Agriculture                            0.35606694
## Argentina.Textile.and.Leather                    0.41813924
## Argentina.Transport.Equipment                    1.06369578
## Turkey.Agriculture                               0.11504126
## Turkey.Textile.and.Leather                       0.11764036
## Turkey.Transport.Equipment                       0.02667530
## Germany.Agriculture                              0.16222512
## Germany.Textile.and.Leather                      0.08244379
## Germany.Transport.Equipment                      0.25807221
##                               Turkey.Agriculture
## Argentina.Agriculture                 1.81066955
## Argentina.Textile.and.Leather         0.48370042
## Argentina.Transport.Equipment         0.03329456
## Turkey.Agriculture                   34.92704803
## Turkey.Textile.and.Leather            2.69291816
## Turkey.Transport.Equipment            0.81210167
## Germany.Agriculture                   2.31122022
## Germany.Textile.and.Leather           1.53837777
## Germany.Transport.Equipment           1.29066963
##                               Turkey.Textile.and.Leather
## Argentina.Agriculture                          3.1173841
## Argentina.Textile.and.Leather                  1.8329024
## Argentina.Transport.Equipment                  0.0790545
## Turkey.Agriculture                             6.9994970
## Turkey.Textile.and.Leather                    40.1671410
## Turkey.Transport.Equipment                     0.9075189
## Germany.Agriculture                            2.0595825
## Germany.Textile.and.Leather                    2.5488967
## Germany.Transport.Equipment                    1.4880228
##                               Turkey.Transport.Equipment
## Argentina.Agriculture                         0.35901126
## Argentina.Textile.and.Leather                 0.43058635
## Argentina.Transport.Equipment                 0.04024626
## Turkey.Agriculture                            1.47711579
## Turkey.Textile.and.Leather                    1.31799873
## Turkey.Transport.Equipment                    3.16041392
## Germany.Agriculture                           0.51211484
## Germany.Textile.and.Leather                   0.63316614
## Germany.Transport.Equipment                   0.56934671
##                               Germany.Agriculture
## Argentina.Agriculture                   1.2364172
## Argentina.Textile.and.Leather           0.5937041
## Argentina.Transport.Equipment           0.0231846
## Turkey.Agriculture                      2.5543089
## Turkey.Textile.and.Leather              1.1093993
## Turkey.Transport.Equipment              0.1151191
## Germany.Agriculture                    29.8763359
## Germany.Textile.and.Leather             1.4593583
## Germany.Transport.Equipment             1.7321726
##                               Germany.Textile.and.Leather
## Argentina.Agriculture                          1.30283802
## Argentina.Textile.and.Leather                  1.15375958
## Argentina.Transport.Equipment                  0.07482343
## Turkey.Agriculture                             1.52213499
## Turkey.Textile.and.Leather                     1.15207241
## Turkey.Transport.Equipment                     0.07448266
## Germany.Agriculture                            5.24719728
## Germany.Textile.and.Leather                   18.95868110
## Germany.Transport.Equipment                    1.51401054
##                               Germany.Transport.Equipment
## Argentina.Agriculture                           4.1208736
## Argentina.Textile.and.Leather                   4.7490351
## Argentina.Transport.Equipment                   0.1932621
## Turkey.Agriculture                              6.1806254
## Turkey.Textile.and.Leather                      9.5069032
## Turkey.Transport.Equipment                      0.6464733
## Germany.Agriculture                             9.6006931
## Germany.Textile.and.Leather                     8.1583150
## Germany.Transport.Equipment                    34.7438192
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{w} \hlkwb{<-} \hlkwd{wwz}\hlstd{(decompr_object)}
\end{alltt}
\end{kframe}
\end{knitrout}
